The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-25 paper/ms.tex
editting the results section

Gas bulk rotation has a noticeable effect on the morphology of the
 \ly line. In this section we discuss the observational implications 
 of these findings.

We start by a quantitative discussion of the line morphology. Here we
follow a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into four groups. In Group I the
red peak is stronger than the blue, in Group II the blue peak is
stronger, in both cases the peaks are symmetrically located around the
line center. In Group III the blue peak also dominates but there is a
overall redward shift of the zero point. Group IV presents two similar
peaks symmetrically located around the zero point. Group V presents
three peaks.

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Ly$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.

As first we see how the width of the line changes using a modified FWHM
explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
rotation increase also the width increase in a factor of $2-3$ in comparison 
with the static case. 'We also take into account the influence of the observer 
viewing angle, we found that observers with a line of sight perpendicular  
to the axis of rotation measure a $15\%$ larger line width than those 
aligned with the rotation axis.'

>>>>

Gas bulk rotation has a noticeable effect on the morphology of the
 \ly line. In this section we discuss the implications of this
 findings for the interpretation of available observational data. Our
 dicussion will focus on the qualitative aspects of diverse
 morpohological features observerd by \cite{Kulas12} ans \cite{Yamada2012}

We follow a classification of $Ly\alpha$ profiles made by
\cite{Kulas12}. They presented observational results for star forming
galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
They classified the observed lines into five groups. In Group I the
red peak is stronger than the blue, while in Group II the blue peak is
stronger, in both cases the peaks are symmetrically located around the
line center. In Group III the blue peak also dominates but there is a
overall redward shift of the zero point. Group IV presents two similar
peaks symmetrically located around the zero point. Group V presents
three peaks.

@@

\section{Conclusions}
\label{sec:conclusions}

In this paper, we have estimated the effects of gas bulk rotation on
the morphology of the Lyman $\alpha$ line in star forming
galaxies. The results are based on the study of an homogeneous sphere
rotating as a solid body. We explored  a range of models by varying
the rotation speed, hydrogen optical depth, dust optical depth and
initial distribution of Ly$\alpha$ photons with respect to the gas
density. As a cross-validation, we obtaine our results from two
independently developed Monte-Carlo radiative transfer codes.

As first we see how the width of the line changes using a modified FWHM
explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
rotation increase also the width increase in a factor of $2-3$ in comparison 
with the static case.
